Meta-analysis of the Interoceptive Accuracy Scale

### 2024-06-09 analysis/Stud1_a.qmd
Study1_a qmd and html
The one that works on my laptop

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---
```{r}
#| message: false
#| warning: false

@@

Murphy (https://osf.io/3m5nh)

@@

Gaggero (2021) (https://osf.io/5x9sg)

@@

Campos (2022) - Study 1 (https://osf.io/j6ef3)

@@

Todd (2022) - https://osf.io/ms354/

@@

Arslanova (2022) - https://osf.io/mp3cy/

@@

Brand (2022) - https://osf.io/xwz6g/

@@

Brand (2023) - https://osf.io/3f2h6/

@@

Lin (2023) - https://osf.io/3eztd
- Note: No tickle because same Chinese character

@@

VonMohr (2023) - Study 3 (https://osf.io/7p9u5/)

@@

:::
## Graph Analysis

@@

compare_mods_h <- function(data) {
  m7 <- lavaan::cfa(m7, data = data)
  m7h2 <- lavaan::cfa(m7h2, data = data)
  m7h1 <- lavaan::cfa(m7h1, data = data)
  m7h3 <- lavaan::cfa(m7h3, data = data)

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---

```{r}
#| message: false
#| warning: false

@@

Murphy (<https://osf.io/3m5nh)>

@@

Gaggero (2021) (<https://osf.io/5x9sg)>

@@

Campos (2022) - Study 1 (<https://osf.io/j6ef3)>

@@

Todd (2022) - <https://osf.io/ms354/>

@@

Arslanova (2022) - <https://osf.io/mp3cy/>

@@

Brand (2022) - <https://osf.io/xwz6g/>

@@

Brand (2023) - <https://osf.io/3f2h6/>

@@

Lin (2023) - <https://osf.io/3eztd> - Note: No tickle because same Chinese character

@@

VonMohr (2023) - Study 3 (<https://osf.io/7p9u5/)>

@@

## Graph Analysis

@@

compare_mods_h <- function(data) {

  fit_model_h <- function(f, data) {
    if(!"Cough" %in% names(data)) {
      f <- str_remove(f, fixed("Cough +"))
    }
    lavaan::cfa(f, data = data)
  }

  m7 <- fit_model_h(m7, data = data)
  m7h2 <- fit_model_h(m7h2, data = data)
  m7h1 <- fit_model_h(m7h1, data = data)
  m7h3 <- fit_model_h(m7h3, data = data)
